\Huge\textbf{Mbrane}\linebreak\linebreak\linebreak \Large\textbf{Final Report}\linebreak\linebreak \linebreak\linebreak \includegraphics[scale=0.1]{feup-logo.png}\linebreak\linebreak \linebreak\linebreak \Large{Logic Programing}\linebreak

### 2019-11-18 docs/report_latex/template.tex
Fixed report and 2 bot bug

%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO complete
\section{Introduction}
\paragraph{}
This project was developed during the Logic Programing Course in the context of the third year of the Integrated Masters in Informatics 
and Computing Engineering at FEUP. The goal was to implement the logic of a board game in Prolog, in this case \textit{Mbrane}.

@@

\subsection{Game state representation} 
Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
boards represented in the game’s data structures. There’s a board predicate that represents the game \textbf{board} itself, a
list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
also a \textbf{board\_blocks} predicate. This predicate is also a list of 9 lists, each one representing a 3 by 3 block of the 
board, this is used to facilitate calculations involving power in each block and influence in adjacent blocks caused 
by the placement of a number in the edge of a block. Finally we have a \textbf{board\_influence} list that stores the values of 
power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
updated accordingly. The predicate used to declare a fresh board is \textit{start\_board(-Board)}, which unifies a variable to a list 
of containing the three boards mentioned above. In order to distinguish both players we determined that Player1 would place 
positive numbers on the board, and Player2 would place negative numbers. This eases the calculations and makes it possible 
to display to the user the which player has controll in each block of the board

@@

\subsection{Board viewing} 
Before each move, the board is displayed on the screen. To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}. This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself. 
The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.
The power of all the blocks is also displayed usinf \textit{display\_power(+Power)}

@@

\paragraph{}
The game is in the final state if no more numbers can be placed on the board, according to placing rule already 
mentioned. We know this usinf the \textit{valid\_moves(+Board, -R)}. If it the Result list is empty, then no more valid
moves can be made, which means the game is in the final state. When this happens the \textit{game\_over(+Board, -Winner)}
predicate calculates the winner of the game.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\paragraph{}
This project was developed during the Logic Programing Course in the context of the third year of the Integrated Masters in Informatics 
and Computing Engineering at FEUP. The goal was to implement the logic of a board game in Prolog, in this case \textit{Mbrane}.

@@

\subsection{Game state representation} 
Although the user can only see one board at a time, in a any phase of the game, there are actually three
boards represented in the game’s data structures. There’s a board predicate that represents the game \textbf{board} itself, a
list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
also a \textbf{board\_blocks} predicate. This predicate is also a list of 9 lists, each one representing a 3 by 3 block of the 
board, this is used to facilitate calculations involving power in each block and influence in adjacent blocks caused 
by the placement of a number in the edge of a block. Finally we have a \textbf{board\_influence} list that stores the values of 
power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
updated accordingly. The predicate used to declare a fresh board is \textit{start\_board(-Board)}, which unifies a variable to a list 
of containing the three boards mentioned above. In order to distinguish both players we determined that Player1 would place 
positive numbers on the board, and Player2 would place negative numbers. This eases the calculations and makes it possible 
to display to the user the which player has controll in each block of the board

@@

\subsection{Board viewing} 
Before each move, the board is displayed on the screen. To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}. This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself. 
The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.
The power of all the blocks is also displayed using\textit{display\_power(+Power)}

@@

\paragraph{}
The game is in the final state if no more numbers can be placed on the board, according to placing rule already 
mentioned. We know this using the \textit{valid\_moves(+Board, -R)}. If the Result list is empty, then no more valid
moves can be made, which means the game is in the final state. When this happens the \textit{game\_over(+Board, -Winner)}
predicate calculates the winner of the game.
